# A. Evaluation and Applied Research Experience {-}

:::{custom-style="note"}
***Note**: Listed in alphabetical order.*
:::

## Timeline of Applied Research and Evaluation Experiences {-}

:::{custom-style="plot"}

```{r echo=FALSE, message=FALSE, warning=FALSE}
project_list %>%
  filter(str_detect(cat, "E")) %>%
  mutate(start = factor(start, levels=timeline),
         end = factor(end, levels=timeline)) %>%
  ggplot()+
  geom_linerange(aes(y=fct_rev(shortname), xmin=start, xmax=end,
                     color=shortname,
                     linetype=status),
                 size=1.5,
                 key_glyph = "path")+
  expand_limits(x=c(3,13))+
scale_color_manual(values=utkpal(project_list %>%
                                     filter(str_detect(cat, 
                                                       "E")) %>%
                                     pull(id)),
                     guide = "none")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 4),
                   drop = FALSE,
                   limits=timeline[-(1:1)])+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 30))+
  scale_linetype_manual(values=c("solid", "dotted"),
                        name="Status")+
  theme_classic()+
    theme(legend.position = "top",
          axis.title = element_blank(),
          axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=8))+
  guides(linetype = guide_legend(override.aes = list(size = 1)))
```
:::


## List of Evaluation and Applied Research Projects {-}


<!-- Tidyr Project - done -->

```{r, child="projects/tidy_table.Rmd", eval=TRUE}

```

<!-- Computer Science Education Project - done -->

```{r, child="projects/cse_table.Rmd", eval=TRUE}

```

<!-- DENA Project : done -->

```{r, child="projects/dena_table.Rmd", eval=TRUE}

```

<!-- Engineering Project  -->

```{r, child="projects/eng_table.Rmd", eval=TRUE}

```

<!-- Fair Chance Project  -->

```{r, child="projects/fairchance_table.Rmd", eval=TRUE}

```

<!-- STARS Project : done-->

```{r, child="projects/stars_table.Rmd", eval=TRUE}

```


<!-- IEP Project : done-->

```{r, child="projects/iep_table.Rmd", eval=TRUE}

```


<!-- gradrates Project: done-->

```{r, child="projects/gradrates_table.Rmd", eval=TRUE}

```


<!-- PHD Students Project : done-->


```{r, child="projects/phdstudents_table.Rmd", eval=TRUE}

```


<!-- SEW Project  : done-->

```{r, child="projects/sew_table.Rmd", eval=TRUE}

```

<!-- Scope 3 Project : done-->

```{r child="projects/scope3_table.Rmd", eval=TRUE}

```

\newline

## Description and Reflection of Experiences {-}

<!-- Tidy Project - done -->

```{r child="projects/tidy_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- CSE Project - done -->

```{r child="projects/cse_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- DENA Project - done -->

```{r child="projects/dena_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- Engineering Project  -->

```{r, child="projects/eng_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- Fair Chance Project  done -->

```{r, child="projects/fairchance_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- STARS 3 Project - done -->

```{r child="projects/stars_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- IEP Project : done-->

```{r, child="projects/iep_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- gradrates Project - done -->

```{r child="projects/gradrates_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- PHD Students Project - done -->

```{r child="projects/phdstudents_evaluation.Rmd", eval=TRUE}

```

\newline

<!-- SEW 3 Project -->

```{r child="projects/sew_evaluation.Rmd", eval=TRUE}

```

\newline


<!-- scope 3 Project -->

```{r child="projects/scope3_evaluation.Rmd", eval=TRUE}

```

\newline

## Materials in Appendix A

1.  [Evaluation Proposal: `r project_head("cse")`](https://drive.google.com/file/d/1PY7MQI44gSy9dnfB0gKz4tuHCTp4ApxS/view?usp=sharing)
2.  [Evaluation Proposal: `r project_head("fairchance")`](https://drive.google.com/file/d/1l0DQb3vqV87Gukmxta9M9tG37GfbkESf/view?usp=sharing)
3.  [Research Proposal: `r project_head("phdstudents")`](https://drive.google.com/file/d/1NFmD_RAIHE0ndhtLfjGP8dnce94HBZCO/view?usp=sharing)


