# B. Statistical Analysis Experience {-}

:::{custom-style="note"}
***Note**: Listed in alphabetical order.*
:::

## Timeline of Statistical Analysis Experience {-}

:::{custom-style="plot"}

```{r echo=FALSE, message=FALSE, warning=FALSE}
project_list %>%
  filter(str_detect(cat, "S")) %>%
  mutate(start = factor(start, levels=timeline),
         end = factor(end, levels=timeline)) %>%
  ggplot()+
  geom_linerange(aes(y=fct_rev(shortname), xmin=start, xmax=end,
                     color=shortname,
                     linetype=status),
                 size=1.5,
                 key_glyph = "path")+
  scale_color_manual(values=utkpal(project_list %>%
                                     filter(str_detect(cat, 
                                                       "S")) %>%
                                     pull(id)),
                     guide = "none")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 4),
                   drop = FALSE,
                   limits=timeline[-(1:1)])+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 30))+
  scale_linetype_manual(values=c("solid", "dotted"),
                        name="Status",
                        drop = FALSE,
                        guide_legend(override.aes = list(size = 1)))+
  theme_classic()+
    theme(legend.position = "top",
          axis.title = element_blank(),
          axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=9))+
  guides(linetype = guide_legend(override.aes = list(size = 1)))
```
:::

## List of Statistical Analysis Experiences {-}

<!-- stats3 Project done-->

```{r, child="projects/stats3_table.Rmd", eval=TRUE}

```

<!-- engineering Project done-->

```{r echo=FALSE, results='asis'}
project("engineering", 3)
```

See *A. Evaluation and Applied Research Experience*

<!-- footprint project: Done-->

```{r, child="projects/footprint_table.Rmd", eval=TRUE}

```

<!-- STARS Project: done -->

```{r echo=FALSE, results='asis'}
project("stars", 3)
```

See *A. Evaluation and Applied Research Experience*

<!-- IEP Project: done-->

```{r echo=FALSE, results='asis'}
project("iep", 3)
```

See *A. Evaluation and Applied Research Experience*

<!-- gradrates Project: done-->

```{r echo=FALSE, results='asis'}
project("gradrates", 3)
```

See *A. Evaluation and Applied Research Experience*

<!-- phdstudents Project -->

```{r echo=FALSE, results='asis'}
project("phdstudents", 3)
```

See *A. Evaluation and Applied Research Experience*

\newline

<!-- advising Project -->

```{r, child="projects/advising_table.Rmd", eval=TRUE}

```

<!-- r handbook Project -->

```{r, child="projects/resm_table.Rmd", eval=TRUE}

```

<!-- roffice Project: done -->

```{r, child="projects/roffice_table.Rmd", eval=TRUE}

```

\newline

## Description and Reflection of Experiences {-}


<!-- stats3 Project: done-->

```{r, child="projects/stats3_stats.Rmd", eval=TRUE}

```

\newline

<!-- Engineering Project : done-->

```{r, child="projects/eng_stats.Rmd", eval=TRUE}

```

\newline

<!-- foorprint : done-->

```{r, child="projects/footprint_stats.Rmd", eval=TRUE}

```

\newline

<!-- STARS Project: done -->

```{r echo=FALSE, results='asis'}
project("stars", 3)
```

See *A. Evaluation and Applied Research Experience*

\newline

<!-- iep Project : done -->

```{r echo=FALSE, results='asis'}
project("iep", 3)
```

See *A. Evaluation and Applied Research Experience*

\newline

<!-- gradrates Project: done -->

```{r, child="projects/gradrates_stats.Rmd", eval=TRUE}

```

<!-- phdstudents Project: consider additional section on data analysis -->

```{r echo=FALSE, results='asis'}
project("phdstudents", 3)
```
See *A. Evaluation and Applied Research Experience*

See *C. Measurement and Instrument Development Experience* 

\newline

<!-- Advising: done -->

```{r echo=FALSE, results='asis'}
project("advising", 3)
```

\newline

<!-- R handbook Project: done-->

```{r, child="projects/resm_stats.Rmd", eval=TRUE}

```

\newline

<!-- R office hours: done-->

```{r, child="projects/roffice_stats.Rmd", eval=TRUE}

```
\newline

## Materials in Appendix B

1.  [Detailed Analysis with Code: `r project_head("stars")` Manuscript](https://drive.google.com/file/d/1pudKUHr2NifTETcYhB6P4xO6pH5gZPAu/view?usp=sharing)
2.  [First-Author Quantitative Paper (published): `r project_head("gradrates")`](https://drive.google.com/file/d/1YvRgqdRBKkphai9J6iELDzpYmfQlTbbb/view?usp=sharing)
3.  [First-Author Quantitative Paper (submitted): `r project_head("iep")`](https://drive.google.com/file/d/1kMfTejCqjfdoJlSCiDX8tNoHPaimrkrP/view?usp=sharing)


