# C. Measurement and Instrument Development Experiences {-}

:::{custom-style="note"}
***Note**: Listed in alphabetical order.*
:::

## Timeline of Measurement and Instrument Development Experiences {-}

:::{custom-style="plot"}
```{r echo=FALSE, message=FALSE, warning=FALSE}

project_list %>%
  filter(str_detect(cat, "M")) %>%
  mutate(start = factor(start, levels=timeline),
         end = factor(end, levels=timeline)) %>%
  ggplot()+
  geom_linerange(aes(y=fct_rev(shortname), xmin=start, xmax=end,
                     color=shortname,
                     linetype=status),
                 size=1.5,
                 key_glyph = "path")+
  scale_color_manual(values=utkpal(project_list %>%
                                     filter(str_detect(cat, 
                                                       "M")) %>%
                                     pull(id)),
                     guide = "none")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 4),
                   drop = FALSE,
                   limits=timeline[-(1:4)])+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 30))+
  scale_linetype_manual(values=c("solid", "dotted"),
                        name="Status")+
  theme_classic()+
    theme(legend.position = "top",
          axis.title = element_blank(),
          axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=9))+
  guides(linetype = guide_legend(override.aes = list(size = 1)))
```
:::

## List of Measurement Tools/Protocols {-}

<!-- tidyr Project: done-->

```{r echo=FALSE, results='asis'}
project("tidy", 3)
```

See *A. Evaluation and Applied Research Experience*
\newline

<!-- CSE Project -->

```{r echo=FALSE, results='asis'}
project("cse", 3)
```
See *A. Evaluation and Applied Research Experience*

\newline


<!-- faculty phd Project -->

```{r child="projects/facultyphd_table.Rmd", eval=TRUE}

```

\newline

<!-- PhD Students Project -->

```{r echo=FALSE, results='asis'}
project("phdstudents", 3)
```

See *A. Evaluation and Applied Research Experience*

\newline

<!-- slam Project -->

```{r child="projects/slam_table.Rmd", eval=TRUE}
```

\newline

<!-- SEW -->

```{r echo=FALSE, results='asis'}
project("sustainable", 3)
```

See *A. Evaluation and Applied Research Experience*

\newline


## Description and Reflection of Experiences {-}

<!-- tidy Project -->

```{r child="projects/tidy_instruments.Rmd", eval=TRUE}

```

\newline

<!-- CSE Project -->

```{r echo=FALSE, results='asis'}
project("cse", 3)
```

See *A. Evaluation and Applied Research Experience*

<!-- faculty phd Project : done-->

```{r child="projects/facultyphd_instruments.Rmd", eval=TRUE}
```

<!-- phdstudents Project -->

```{r echo=FALSE, results='asis'}
project("phdstudents", 3)
```

See *A. Evaluation and Applied Research Experience*

<!-- slam Project: done -->

```{r echo=FALSE, results='asis'}
project("slam", 3)
```
\newline

<!-- SEW Project: done -->

```{r child="projects/sew_instruments.Rmd", eval=TRUE}
```
\newline

## Materials in Appendix C

1.  [Survey Instrument: `r project_head("sustainable")`](https://drive.google.com/file/d/1ogXJLEvtxLhulF43UTEW-HG_W-9xyjuc/view?usp=sharing)
2.  [Interview Protocol: `r project_head("dena")`](https://drive.google.com/file/d/1fLIQ0j286_w_BKXgR-72LWojv1_MpRnP/view?usp=sharing)
3.  [Assessment: `r project_head("slam")`](https://drive.google.com/file/d/1dSqzienXFhghBZrkkUZzzlvctpFG0-E_/view?usp=sharing)

